Datasets

### 2019-01-30 scripts/01-datasets/README.Rmd
update docs
update link to results in readme
fix relative paths

@@

```{r results = 'asis'}
dynbenchmark::knit_nest("02-synthetic")
```

```{r results = 'asis'}
dynbenchmark::knit_nest("04-dataset_characterisation")
```

>>>>

The results of this experiment are available [here](`r dynbenchmark::link_to_results()`).

@@

```{r results = 'asis'}
dynbenchmark::knit_nest("02-synthetic")
```
`
```{r results = 'asis'}
dynbenchmark::knit_nest("04-dataset_characterisation")
```
